News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-05 rupnik2015.tex
paper overview revised

The paper is organized as follows: we first provide an overview of the system as a whole (Section ~\ref{sec:pipeline}), followed by details on the cross-lingual similarity computation and our approach to linking clusters. We first introduce the problem of cross-lingual similarity computation (Section~\ref{sec:crosslingual}), which is followed by several approaches for measuring cross-lingual similarity (Section~\ref{sec:models}) and then the algorithms for matching clusters in different languages (Section~\ref{sec:linking}).  To improve readability, we will describe relevant related work for each module in its corresponding section. Finally, we present and interpret the experimental results, give conclusions and describe promising future directions.

@@

\section{Evaluation}

>>>>

The paper is organized as follows: we first provide an overview of the system as a whole (Section~\ref{sec:pipeline}), which includes a subsection that summarizes the main system requirements in Section~\ref{sec:sysreq}. We then present related work in Section~\ref{sec:related}. The related work covers work on cross-lingual document similarity as well as work on cross-lingual cluster linking. In Section~\ref{sec:crosslingual} we introduce the main problem of cross-lingual document similarity computation, which is followed by an overview of the models that we considered in Section~\ref{sec:models}. We then establish necessary notation in Section~\ref{sec:notation} and proceed with four subsections that describe the main cross-lingual similarity approaches in detail. The approach in Section~\ref{sec:kmeans} serves as a baseline, and the approaches in Section~\ref{sec:CCA} and Section~\ref{sec:LSI} serve as the basis on which we proposed a new approach presented in Section~\ref{sec:hublang}. In Section~\ref{sec:linking} we introduce the central problem of cross-lingual linking of clusters of news articles and our approach that combines the cross-lingual similarity functions with knowledge extraction based techniques. Finally, we present and interpret the experimental results in Section~\ref{sec:evaluation} and discuss conclusions and point out several promising future directions.

@@

\section{Evaluation}\label{sec:evaluation}
